% Autor: Betti Oesterholz
% erstellt: 18.12.2010
% Dies ist der Handzettel zum Fib development Unternehmen
%
% Copyright (c) 2010 Betti Oesterholz
%
% Permission is granted to copy, distribute and/or modify this document
% under the terms of the GNU Free Documentation License, Version 1.2 or
% any later version published by the Free Software Foundation;
% with no Invariant Sections, no Front-Cover Texts, and no Back-Cover Texts.
%
% A copy of the license is included in the file ``fdl.tex'' .
%


\documentclass[12pt,a4paper]{article}
\pagestyle{empty} %keine Seitennummerierung
\usepackage{a4wide} % besser den Platz nutzen (kleinere R"ander)
%\usepackage{ngerman} % Silbentrennung nach neuer Rechtschreibung
\usepackage[T1]{fontenc} % Type 1 Schriften
\usepackage{times} % Da die Standard-LaTeX-Schrift bei mir mit Acrobat nicht funkt.
\usepackage[ansinew]{inputenc} % Verwendung von Umlauten
%\usepackage{scrpage2} % Seitenformat
%\usepackage{titletoc}
%\usepackage{titlesec}
\usepackage{listings} % Programm-Listing
%\usepackage [usetoc]{titleref} 
\usepackage{graphicx} % Einbindung von Graphiken
\usepackage{url} % URLs durch \url{}
%\usepackage{bibgerm} % deutsche Bibliographie
%\usepackage{txfonts}%Paket fr das nat Symbol
\usepackage{multicol}
%\usepackage{makeidx}%for the index
%\usepackage{longtable}
%\usepackage{amsmath}%mathematikumgebung {equation*} usw.

% Seitenstil festlegen
%\pagestyle{useheadings}%or: headings

% naehste vier Zeilen: Format des Inhaltsverzeichnisses
%\titlespacing{\section}{0pt}{5cm}{5cm}%spacing by sections {in front}{above}{below}
%\dottedcontents{section}[1.5em]{\addvspace{1.0em}}{1.3em}{0.7pc}
%\dottedcontents{subsection}[3.8em]{}{2.2em}{0.7pc}
%\dottedcontents{subsubsection}[7.0em]{}{3.1em}{0.7pc}

%\setcounter{secnumdepth}{4}%%nummerierung der Unterabschnitte bis Tiefe


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Beginn des Dokuments
%\makeindex

\begin{document}

%\renewcommand{\sectionmark}[1]{\markboth{#1}{}}
%\pagenumbering {Roman}
%\automark{section}
%\pagestyle{scrheadings} % individ. Seitenlayout
%\setheadsepline{0.4pt}
%\ihead{} % Titelzeile innen
%\ohead{} % Titelzeile aussen
%\chead{\slshape \headmark}  % Titelzeile mitte
%\cfoot{\thepage} % Fusszeile mitte

% braucht man ein Inhaltsverzeichnis, so sind die naehsten drei Zeilen auszukommentieren
%\setcounter{tocdepth}{3}
%\tableofcontents
%\clearpage

% Vorschlag fr Titelzeile:
% Bei umfangreicheren Dokumenten
%\ihead{\slshape \headmark } % Darstellung von Sectionnummer und -name
%\ohead{}
%\chead{}


%\pagenumbering{arabic}


\ \vspace{-2.5cm}
\begin{center}
	\LARGE\bf Fib development\\
\end{center}

\bigskip\noindent
The enterprise Fib development serves as the legal framework for the promotion of the Fib project. It has the character of a research institute, so that not the profit is most important, but the development of the Fib multimedia system.


\section{Offer}

The Fib multimedia system offers many companies and organizations, that use multimedia data or are based on its use, new market potentials. So that these companies can take better advantage of the benefits resulting from Fib, the central coordination of information, research and development of Fib in one company (Fib development) is advantageous.


\section{Your gain}

With the access to information about Fib companies that use Fib, can improve their products and gain a competitive edge.

The accumulation of development and responsibility for Fib in one external company has the following benefits for other companies:
\begin{itemize}
 \item the inventor and major specialist Betti \"{O}sterholz is centrally involved in the development of the Fib system
 \item compatibility of the Fib based solution of different companies
 \item establishing of an independent standard for Fib
 \item lower costs for one company, because the funding is distributed over several companies
 \item accessible information pool for all
 \item greater efficiency through specialization
 \item individual companies may not be accused of an influence on the market with Fib (protection against image damage)
% \item Einsparungen beim Personal und Aufwand, da nur ein Format f"ur mehrere Multimediainhalte zu ber"ucksichtigen ist.
\end{itemize}


\section{Company philosophy: \newline For diversity. For knowledge. For people!}

It is the basic goal of the company to make peoples life better by using more diversity. Hence the creation of new knowledge is needed, from which the new diversity can emerge.

Fib is a system that builds on diversity. To let people benefit from this this diversity, various methods are used to promote the development and distribution of the Fib system.


\newpage
\section{How you can help Fib}

The main source of income for the company should be project funding, with additional product-related services offered for money.


\subsection{Investments}

Investment in Fib development will be for the benefit of the further development and distribution of Fib, so that everyone who uses Fib will gain from it.

%Unbound transfers, which should be for the Fib system in general, can be made directly to the company account.
You are also welcome to create contracts with us for the payments, to regulate the use of the funds.


% \paragraph{Business bank account:}
% 
% \begin{tabbing}
% Account Owner: \hspace{1cm}\= Betti Susanne \"{O}sterholz\\
% Bank:\> Mittelbrandenburgische Sparkasse in Potsdam\\
% Bank identifier code: \> 160 500 00\\
% Account number: \> 10000 152 77\\
% \end{tabbing}
% \ \vspace{-1.0cm}


\subsection{More ways to help}
%Hilfe: Informationen, Entwicklung (Rat und Tat), neue Operatoren, Kundenkontakte

You can also support the development and distribution of Fib through other means.
This can be done for example by:
\begin{itemize}
 \item informing others about the Fib system
 \item bring us in contact to customers/investors
 \item suggestions for improving the Fib system
 \item help for the development of Fib
\end{itemize}
\ \vspace{-0.60cm}

\subsection{Fib development}

\begin{tabbing}
\hspace{35mm}\=\hspace{20mm} \=\kill
\textbf{Holder:} \> Betti Susanne \"{O}sterholz \>\\
 \> \>\\
\textbf{Address:}\> Falkenhorst 34 \>\\
	\>14478  Potsdam \>\\
	\>germany \>\\
	\>Phone: \>+49 0331 6012886\\
	\>E-Mail: \>\url{Oesterholz@fib-development.org}\\
	\>Web page: \>\url{www.fib-development.de}\\
%	\>Private web page: \>\url{www.BioKom.info}\\
% \> \>\\
\textbf{VAT number:}\>DE 274116427 \>\\
\end{tabbing}



\end{document}


